BOLD Parameter Estimation Using Particle Filters

### 2010-08-13 doc/thesis/results.tex
changes to thesis

\chapter{Simulation}
\label{sec:SimulationResults}
Two levels of simulation are discussed in this section. First the simulation of single time series
and second, a slice of simulated FMRI time series. The single time series tests
are necessary to investigate the power of particle filters in 
identifying the BOLD model in a noisy environment. If the particle filter is unable
to get back to the \emph{true} time-series in spite of noise then the particle filter
will not be useful. Additionally, determination of reasonable parameters from the
time-series is also desirable. The reason to then simulate an entire slice is that
Physics-Oriented Simulated Scanner for Understanding MRI (POSSUM)
models noise more realistically, for instance by adding noise in the frequency domain. 
It also provides insight into the applicability of particle filters in modeling the BOLD 
signal on a large scale. Both sorts of tests are usefull in determining the
consistency of the particle filter. For the single voxel tests, each test will
actually be performed eleven different times, each with a new noise realization.
If runs fail to have consistent estimates of the underlying BOLD signal, then
this would indicate a large variance error in the model. Similarly, in the
Possum simulation there are actually only four discrete parameter sets driving the time-series.
Nevertheless each voxel will have a different tissue composition and a different
noise realization. Therefore the Possum simulation should also provide a good
test of the consistency of the BOLD model.

>>>>

\chapter{Simulation}
\label{sec:SimulationResults}
Two levels of simulation are discussed in this section. First the simulation of single time series
and second, a slice of simulated FMRI time series. The single time series tests
are necessary to investigate the power of particle filters in 
identifying the BOLD model in a noisy environment. If the particle filter is unable
to get back to the \emph{true} time-series in spite of noise then the particle filter
will not be useful. Additionally, determination of reasonable parameters from the
time-series is also desirable. An entire slice is then simulated using 
Physics-Oriented Simulated Scanner for Understanding MRI (POSSUM) which
models noise more realistically. POSSUM also provides insight into the 
applicability of particle filters in modeling the BOLD 
signal on a large scale. Both sorts of tests are usefull in determining the
consistency of the particle filter. For the single voxel tests, each test will
actually be performed eleven different times, each with a new noise realization.
If runs fail to have consistent estimates of the underlying BOLD signal, then
this would indicate a large variance error in the model. Similarly, in the
Possum simulation there are actually only four discrete parameter sets driving the time-series.
Nevertheless each voxel will have a different tissue composition and a different
noise realization. Therefore the Possum simulation should also provide a good
test of the consistency of the BOLD model.
